Sufficient Conditions for Reachability in Automata Networks with Priorities

### 2014-03-27 parts/sa.tex
sequential under-approximation

The reachability property studied so far concern a single process, \ie{} the
local state of a single component.
However, we remark that the reachability of a partial or global state can be
addressed with the very same analysis by introducing a dedicated cooperative
sort in the scope of the PH semantics with $2$ classes of priorities.

@@

\subsection{Sequential reachability}

The sufficient condition for the reachability of a process from a given context
can be extended for the successive reachability of several processes ($a_i$,
then $b_j$, etc.) in the following manner.

\todo{}

\begin{definition}
\label{def:lastprocs}
\end{definition}

\begin{theorem}[Sequential under-approximation]
\label{thm:ordered-ua}
Given a context $\ctx$ and an objective sequence $\w =
P\concat\w'\in\OS$,
$\uconcr(P)\neq\emptyset \wedge
	\muconcr_{\ctx'}(\w')\neq\emptyset
	\Longrightarrow \uconcr(\w)\neq\emptyset$,
where $\ctx' = \procs(\mycwB{\ctx}{P})\Cap\lastprocs(P)$
\end{theorem}

>>>>

The reachability property studied so far concern a single process at a time.
However, we remark that the reachability of a partial or global state can be
addressed with the very same analysis by introducing a dedicated cooperative
sort in the scope of the PH semantics with $2$ classes of priorities.

@@

\subsection{Sequential under-approximation}

In this section, we briefly explain an alternative sufficient condition that
progressively takes into account the successive objectives, instead of
considering all of them at a time, as it is done in the previous sections.
Because objectives are taken into account individually, such an approach
considers only a subset of scenarios.
However, because each iteration focuses on a smaller part of the network, this
sequential under-approximation may be more conclusive.

Let us define a sequence of objective $\w=\obj{a_i}{a_j}\concat\w'$ with
$a_i\neq a_j$ and a state $s\in L$ with $\get{s}{a}=a_i$.
One can remark that any scenario reaching $a_j$ necessarily includes one of the
bounce sequence in $\BS(\obj{a_i}{a_j})$, and in particular,
any minimal scenario reaching $a_j$ ends in a state where $a_j$ is present but
also the hitter of the last of one bounce sequence in $\BS(\obj{a_i}{a_j})$.
If such hitter $b_k$ is in a cooperative sort $b\in\cs$, it also means that one of the sub-state
in $\csState(b_k)$.
\pref{def:lastprocs} defines $\lastprocs(\obj{a_i}{a_j})$ as the set of set of
processes that may be present just after reaching $a_j$.

From \pref{th:approxinf}, we can deduce that
for any scenario $\delta$ in $\uconcr(P)$,
there exists a set of processes $ps\in\lastprocs(P)$
such that $ps \subset (s\play\delta)$.
Hence, if $\muconcr_{\ctx'\Cap ps}(\w')\neq\emptyset$,
with $\ctx'=\ctx\Cap\procs(\mycwB{\ctx}{P})$,
there exists a scenario $\delta'$ concretizing $\w'$ from the
state $(s\play\delta)$.
Therefore, the scenario $\delta\concat\delta'$ concretizes
$\w$.

\begin{definition}[$\lastprocs$]
\label{def:lastprocs}
Given an objective $\obj{a_i}{a_j}$, $\lastprocs:
\Obj\to\powerset(\powerset(\Proc))$ is
defined such that, $\forall lps\in\lastprocs(\obj{a_i}{a_j})$, 
$lps\in\powerset(\Proc)$,
\begin{enumerate}
\item $\{\hitter{\zeta_{\card\zeta}}\} \subset lps$;
\item $\forall b_j\in lps, b\in\cs, \exists ps\in\csState(b_j): ps\subset lps$;
\item $\forall b_j\in lps, b\in\cs, 
		\forall ps\in\csState(b_j),
			\exists lps'\in\lastprocs(\obj{a_i}{a_j}),
				ps\subset lps'$;
\item $\nexists lps'\in\lastprocs(\obj{a_i}{a_j}): lps'\subset lps \wedge
									lps'\neq lps$.
\end{enumerate}
\end{definition}

\begin{theorem}[Sequential under-approximation]
\label{thm:ordered-ua}
Given a context $\ctx$ and an objective sequence $\w =
P\concat\w'\in\OS$,
$\uconcr(P)\neq\emptyset \wedge
	\forall ps \in\lastprocs(P),
	\muconcr_{\ctx'\Cap ps}(\w')\neq\emptyset
	\Longrightarrow \uconcr(\w)\neq\emptyset$,
where $\ctx' = \ctx\Cap\procs(\mycwB{\ctx}{P})$.
\end{theorem}
\begin{proof}
If $\uconcr(P)\neq\emptyset$,
for all $s\in L, s\subset\ctx$,
there exists a scenario $\delta\in\uconcr(P)\cap\Sce(s)$;
from \pref{def:lastprocs} and proof of \pref{th:approxinf},
$\exists ps\in\lastprocs(P)$ such that
$(s\play\delta)\subset\ctx'\Cap ps$.
Hence, if $\muconcr_{\ctx'\Cap ps}(\w')\neq\emptyset$,
there exists a scenario $\delta'\in\muconcr_{\ctx'\Cap ps}(\w')$ such that
$\delta'\in\Sce(s\play\delta)$.
Hence, $\delta\concat\delta'$ is a scenario playable in $s$.
Therefore, for all $s\in L, s\subset\ctx$, there exists a scenario
concretizing $\w$.
Hence, $\uconcr(\w)\neq\emptyset$.
\end{proof}
